This section describes the signal extraction strategy. In order to describe the data, we consider three contributions to the \Mbb{} distribution:  
\begin{itemize}
  \item Signal \Hbb from either VBF or ggF production
  \item Resonant \zjets{} from QCD and EW production
  \item Non-resonant processes dominated by QCD multi-jet production
\end{itemize}

The shapes of the signal and \zjets{} contributions are each parameterized by a Bukin function as described in \ref{sec:vbf-parsigz}. The non-resonant background is taken from data using a fit with an analytical function in the \Mbb{} sidebands of the signal regions and control region as described in Section~\ref{sec:vbf-nonres}.
The signal strength is measured with a profile likelihood fit performed simultaneously for all signal and control regions.

It is noteworthy that the $Z$ normalization is treated as a nuisance parameter in the fit. The \zjets{} contribution plays an important role in the overall fitting procedure due to the fact that it comprises a significant fraction lower \Mbb{} sideband, yet the sideband does not extend to low enough \Mbb{} values to reliably constrain its contribution using the shape templates.  Therefore, the non-resonant background fit can be partially compensated by the $Z$-yield and vice-versa.  To mitigate the impact of this degeneracy, we could fix the contributions of \zjets{} in the fits to predictions from MC.  However, our \zjets{} MC is only leading order ($Z+$2 partons), and large or varying $k$-factors may be present in the different BDT regions.  Therefore, we assume no prior knowledge of $Z$ contribution in all BDT regions and allow the contribution to float in the profile likelihood fit. This is the most conservative strategy and yields the largest decrease in overall sensitivity.

To validate the fit closure and conduct sensitivity study, Asimov datasets are constructed. An Asimov dataset is the sum of the Higgs signal, \zjets{} process and the analytical non-resonant background. The normalization of the Higgs signal and \zjets{} components is the product of the expected strength and the yield taken from MC prediction.

%The normalization of the non-resonant background is estimated by scaling the number of events of the 0-tag sample by the ratio of the events in the sidebands for the 2- and 0-tag samples. Specifically $B$ is given by $N_{\rm 0~tag, mw}\times \frac{N_{\rm 2~tag, sb}}{N_{\rm 0~tag, sb}}$ where  $N_{\rm 0~tag, mw}$ is the number of events from the 0-tag sample in the Higgs mass window, and $N_{\rm 2(0)~tag, sb}$ is the number of events in the side-band regions for 2(0)-tag sample.

%\subsection{Treatment of \zjets{} contribution}
%\label{sec:vbf-ztreat}

\subsection{Signal and \zjets Parameterization}
\input{chapters/VBF/signalandz}
\subsection{Non-resonant Background Estimation}
\input{chapters/VBF/fitbkgds}
\subsection{Uncertainties}
\input{chapters/VBF/uncertainties}
\subsection{Binned Likelihood Maximization}
\input{chapters/VBF/likelihood}


