One critical research area at the Large Hadron Collider (LHC) is the search for highly Lorentz boosted Higgs bosons produced from the Standard Model (SM)~\cite{Sirunyan:2017dgc} or from beyond the SM processes~\cite{Aaboud:2017ecz,Aaboud:2017ahz,Aaboud:2017yqz,Aaboud:2016xco,Khachatryan:2016cfa,Sirunyan:2017nrt}.  As the branching ratio for the Higgs to decay into bottom quark pairs dominates the total decay rate, the boosted $H\rightarrow b\bar{b}$ channel is often the most sensitive.  Algorithms for identifying jets resulting from bottom quark fragmentation are very powerful, so the main background for boosted Higgs boson searches contains real $b$-quarks.  The main contribution to this background is gluon splitting to $b$-$\bar{b}$ pairs at small opening angles since the angle between the $b$ quarks in $H\rightarrow b\bar{b}$ scales with $m_H/p_H$.  The $g\rightarrow b\bar{b}$ process also contributes to many other important SM measurements and searches, providing a source of additional real $b$-quark jets that can fake a signal where $b$ quarks originate from elsewhere.  


The modeling of $g\rightarrow b\bar{b}$ fragmentation is complex and interesting in its own right.  The significant mass of the $b$-quark modifies the usual quantum chromodynamic (QCD) splitting functions.  Trijet events from LEP~\cite{Barate:1998vs,Abbiendi:2000zt,Abreu:1999qh} and SLD~\cite{Abe:2001csa} provide valuable information on the rate of $g\rightarrow b\bar{b}$, but do not constrain the differential properties of the fragmentation in the small opening angle regime.  Previous measurements that include the the $b\bar{b}$ final state at the S$p\bar{p}$S, Tevatron, and LHC using inclusive~\cite{Albajar:1993be,Albajar:1990zu,Aaboud:2017vqt,Khachatryan:2011wq,Chatrchyan:2012hw,Aad:2011rr,Abbott:1999se,Aaltonen:2007zza,Abbott:1999wu,Abachi:1994kj,Khachatryan:2011wq,Aaij:2017pvu,Aaij:2010gn,Aaij:2013noa,Aaij:2012jd,Aaij:2010gn,Aad:2012jga,Aad:2011sp,Aad:2015duc,Khachatryan:2010yr,Acosta:2004yw,ATLAS:2013cia}, multijet~\cite{Aaboud:2016jed,ATLAS:2011ac,Chatrchyan:2012dk}, and associated production~\cite{Aad:2013vka,Aad:2014dvb,Chatrchyan:2014dha,Abazov:2014fka,Abazov:2013uza,Abazov:2015aha,Aaltonen:2013ama,Aaltonen:2009qi,Aaltonen:2008mt,Chatrchyan:2013zja,Chatrchyan:2013zja} topologies have focused on well-separated quark pairs and were limited in their kinematic reach due in part to limited dataset sizes and low $\sqrt{s}$.

The high transverse momentum and low angular separation regime for $g\rightarrow b\bar{b}$ can be probed at the LHC using large-radius jets with $b$-tagged subjets. This topology has been used for calibrating $b$-tagging in dense environments~\cite{ATLAS-CONF-2016-039,ATLAS-CONF-2016-002,CMS:2013vea} and has been studied phenomenologically~\cite{Anderle:2017qwx,Ilten:2017rbd}.  This measurement builds on these studies to perform the first differential cross-section measurement of the $g\rightarrow b\bar{b}$ at high transverse momentum inside jets.  Small-radius jets built from charged particle tracks are used as proxies for the $b$-quark fragmentation and allow for a precision probe of the small opening angle regime.

