\label{sec:gbb-obj}

\subsubsection{Primary Vertex and Track Selection}
The primary vertex is selected in the same way as defined in Sec.\ref{sec:vbf-objsel}.
Tracks which are used in this study to build track jets need to pass the following requirements:
\begin{itemize}
    \item $p_T>$ 0.5 GeV
    \item Number of Pixel hits greater than 1
    \item Number of SCT hits greater than 6
    \item $|d_0|<1$mm, with respect to primary vertex
    \item $|z_0\sin(\theta)|<1$mm, with respect to primary vertex
\end{itemize}

\subsubsection{Jet Selection}
In this study we use $R$=1.0 calorimeter jets and $R=0.2$ track jets. Calorimeter jets are clustered in $y-\phi$ space using the anti-$k_t$~\cite{Cacciari:2008gp} algorithm with $R=1.0$ reconstructed from topological calorimeter clusters~\cite{TopoClusters} using the local cluster weighting (LCW) algorithm \cite{EndcapTBelectronPion2002} and calibrated to account for the detector response. Track jets are reconstructed clustering inner detector tracks using the anti-$k_t$ algorithm and are required to have at least two tracks.

\noindent The $R = 1.0$ calorimeter jets are groomed using the trimming procedure~\cite{Krohn:2009th}, whereupon the $k_{t}$ sub-jets ~\cite{Cacciari200657} with $R=0.3$ are discarded if the fractional $p_{T}$ of the subject relative to the whole $R=1.0$ jet satisfies $f_\text{ cut}<0.05$.  

\noindent The $R=0.2$ track jets are subject to the following selection, 
\begin{itemize}
	\item $p_T>$10 GeV
	\item $|\eta|<2.5$	
	\item The track jet originates from the primary vertex (OriginIndex==0)
\end{itemize}

\subsubsection{$b$-tagging}

Jets are identified as $b$-jets using the multivariate discriminant \textit{MV2c10} \cite{btag} which includes impact parameter and secondary vertex information as inputs. The chosen \textit{MV2c10} working point corresponds to an average $b$-tagging efficiency of 60\% for $b$-jets in simulated $t\bar{t}$ events.  

\subsubsection{Ghost Association of Jets}

Ghost association~\cite{area} is adopted to associate $R=0.2$ track jets to $R=1.0$ jets. Similar to the ghost association of tracks to jet described in Sec.\ref{sec:vbf-objsel}, 4-vectors of the track jets are added to the inputs of the calorimeter jet clustering algorithm has their $p_T$ set to an infinitesimal amount.  R=1.0 calorimeter jet clustering is then performed. R=0.2 track jets which are clustered into the R=1.0 calorimeter jet are then considered to be associated to the $R=1.0$ jet.  

\subsubsection{Flavor Labeling of Jets in Simulation}

The flavor content of the track jet is determined by ghost matching truth particles (weakly decaying $b$-hadrons and $c$-hadrons) to the track jet. For each jet, if a $b$-hadron is found to be associated to the jet, then the jet is labeled as a $b$-jet.  If there are no $b$-hadrons but a $c$-hadron is found to be associated to the jet, then the jet is labeled as a $c$-jet. Otherwise, the jet is labeled as a light-flavored jet. 

\subsubsection{Truth Jets}
All final state truth particles (ignoring truth pileup) with mean lifetimes longer than 30 ps, except muons and neutrinos, are used as input to the clustering of truth jets. Same clustering algorithms and parameters are used as their reconstructed counterparts except that the truth $R=1.0$ jets do not receive trimming. 
